Compensated de Casteljau algorithm in \(K\) times the working precision

### 2018-05-16 doc/paper.tex
Isolating Tikz images as standalone PDFs.
This is both a way to "streamline" the building of the main paper
and an effort to "pass" the build on EES.

%% H/T: https://tex.stackexchange.com/a/99051/32270
\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{box} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text centered, draw=black]
\tikzstyle{empty-box} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text width=0.05\textwidth]
\tikzstyle{empty-box-vert} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text centered, text height=0.001\textwidth]
\tikzstyle{line} = [draw, -latex']

@@

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
  \node (b0) {\(\widehat{b}^{(n)}\)}
    child {node (b1) {\(\widehat{b}^{(n - 1)}\)}
      child {node (b2) {\(\widehat{b}^{(n - 2)}\)}
        child {node (bdots) {\(\vdots\)}
          child {node (bn) {\(\widehat{b}^{(0)}\)}}
          child {node (ln) {\(\ell^{(0)}\)}}
        }
        child {node (ldots) {\(\vdots\)}}
      }
      child {node (l2) {\(\ell^{(n - 2)}\)}}
    }
    child {node (l1) {\(\ell^{(n - 1)}\)}};
  %%
  \path (b1) -- (l1) node [midway] {\(+\)};
  \path (b2) -- (l2) node [midway] {\(+\)};
  \path (bn) -- (ln) node [midway] {\(+\)};
  %% eb == exact b
  \node [right of=b0] (eb0) {\(b^{(n)}\)}
    child {node (eb1) {\(b^{(n - 1)}\)}
      child {node (eb2) {\(b^{(n - 2)}\)}
        child {node (ebdots) {\(\vdots\)}
          child {node (ebn) {\(b^{(0)}\)}}
        }
      }
    };
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Local round-off errors}
\label{fig:loc-err-accumulate}
\end{figure}

@@

\begin{figure}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\cdb{1}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\cdb{2}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\cdb{3}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\cdb{1}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\cdb{2}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\cdb{3}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\cdb{1}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\cdb{2}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\cdb{3}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\label{fig:error-filtration}
\end{figure}

>>>>

@@

\begin{figure}
  \includegraphics[width=0.375\textwidth]{tikz_local_err.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Local round-off errors}
  \label{fig:loc-err-accumulate}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{tikz_filtration.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Filtering errors}
  \label{fig:error-filtration}
\end{figure}
